Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-03-03 VegOzone.tex
Input of supplementary material - final pdf needs to be seperated

A climatology derived for global irradiance $Q_0$ is shown in Appendix Fig.~\ref{fig:global_rad_clim}a) for both, climatological average of hourly maximum $\left<Q_0^\mathrm{max}\right>$, minimum $\left<Q_0^\mathrm{min}\right>$, and mean $\left<Q_0^\mathrm{mean}\right>$ irradiance observed at Svanvik. In agreement with the geometrically derived sunshine duration shown in Appendix Fig.~\ref{fig:sunlight_fennoscandia}, $\left<Q_0^\mathrm{max}\right>$ approaches zero in December/January commonly known as polar night and reaches its maximum in June/July commonly referred to as midnight sun conditions. The highest observed $\left<Q_0^\mathrm{max}\right>$ is about $800\,\unit{W\,m^{-2}}$, while on average $\left<Q_0^\mathrm{mean}\right>$ it is about $450\,\unit{W\,m^{-2}}$ (regularly reached in May--July). The maximum of the climatological minimum $\left<Q_0^\mathrm{min}\right>$ lies at about $200\,\unit{W\,m^{-2}}$.

@@

>>>>

A climatology derived for global irradiance $Q_0$ is shown in Appendix Fig.~\ref{fig:global_rad_clim}a) for both, climatological average of hourly maximum $\left<Q_0^\mathrm{max}\right>$, minimum $\left<Q_0^\mathrm{min}\right>$, and mean $\left<Q_0^\mathrm{mean}\right>$ irradiance observed at Svanvik. In agreement with the geometrically derived sunshine duration shown in Supplement Fig.~\ref{fig:sunlight_fennoscandia}, $\left<Q_0^\mathrm{max}\right>$ approaches zero in December/January commonly known as polar night and reaches its maximum in June/July commonly referred to as midnight sun conditions. The highest observed $\left<Q_0^\mathrm{max}\right>$ is about $800\,\unit{W\,m^{-2}}$, while on average $\left<Q_0^\mathrm{mean}\right>$ it is about $450\,\unit{W\,m^{-2}}$ (regularly reached in May--July). The maximum of the climatological minimum $\left<Q_0^\mathrm{min}\right>$ lies at about $200\,\unit{W\,m^{-2}}$.

@@

\input{supplements/VegOzone_supplement}

### 2021-03-03 supplements/VegOzone_supplement.tex
Input of supplementary material - final pdf needs to be seperated

\begin{figure*}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs}
  \caption{S1 Multi-annual mean of daily mean ozone at observation sites in Fennoscandia. The large spread in case of Svanvik and Janiskoski is due to the lower statistics. All climatologies peak in spring, with peak values in April. The annual average ozone concentration \chem{\left<[O_3]\right>} at Svanvik is $6.6\,\unit{ppb}$ lower than at the sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN).}
  \label{fig:ozone_climatology_fenoscandic_obs}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{test_fennoscandia}
  \caption{Maximum daily sun shine duration based on geometrical calculations at different sites in Fennoscandia. Midnight sun conditions at Jergul/Karasjok and Svanvik prevail from the end of May until the end of July, while at Esrange and Pallas they only prevail from the beginning of June until mid of July.}
  \label{fig:sunlight_fennoscandia}
\end{figure*}

@@

\begin{figure*}[t]
\include{supplement_do3se-parameterization_v2.pdf}
\label{tab:do3se_mm_param}
\end{figure*}

>>>>

\graphicspath{{pictures/}}          % graphics
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\clearpage
\setcounter{page}{1}
\setcounter{figure}{0}

%\begin{figure*}[t]
%  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs}
%  \caption{Multi-annual mean of daily mean ozone at observation sites in Fennoscandia. The large spread in case of Svanvik and Janiskoski is due to the lower statistics. All climatologies peak in spring, with peak values in April. The annual average ozone concentration \chem{\left<[O_3]\right>} at Svanvik is $6.6\,\unit{ppb}$ lower than at the sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN).}
%  \label{fig:ozone_climatology_fenoscandic_obs}
%\end{figure*}

\begin{figure}[t]
  \includegraphics[width=12cm]{test_fennoscandia}
  \caption{Maximum daily sun shine duration based on geometrical calculations at different sites in Fennoscandia. Midnight sun conditions at Jergul/Karasjok and Svanvik prevail from the end of May until the end of July, while at Esrange and Pallas they only prevail from the beginning of June until mid of July.}
  \label{fig:sunlight_fennoscandia}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=1\textwidth]{supplements/supplement_do3se-parameterization_v2}
\label{tab:do3se_mm_param}
\end{figure*}
